Wavelets

### 2019-03-15 Wind_analyses.Rmd
progress..

## Load in the sea surface temperatue datasets
## See the Dectect_MCS.Rmd script for more info. The datasets loaded here are only for temperatures collected between the years 1992-2016. However if a longer time series is required changes may  be made to the Dectect_MCS.Rmd script (line 136)

load("Data/overlap_ts.RData")
load("Data/insitu_MUR.RData")
load("Data/insitu_OISST.RData")
load("Data/insitu_G1SST.RData")
load("Data/insitu_K10.RData")

@@

temp_wind_MUR <- temp_wind(df = MUR_fyears)
temp_wind_SACTN <- temp_wind(df = SACTN_fyears)
temp_wind_OISST <- temp_wind(df = OISST_fyears)
temp_wind_G1SST <- temp_wind(df = G1SST_fyears)
temp_wind_K10 <- temp_wind(df = K10_fyears)
```

@@

source("functions/wind.rose.R")

renaming_func <- function(df){ 
  renaming <- df %>% 
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ)
}

temp_wind_MUR <- renaming_func(df = temp_wind_MUR)
temp_wind_SACTN <- renaming_func(df = temp_wind_SACTN)
temp_wind_OISST <- renaming_func(df = temp_wind_OISST)
temp_wind_G1SST <- renaming_func(df = temp_wind_G1SST)
temp_wind_K10 <- renaming_func(df = temp_wind_K10)

## Plotting function

p.wr2 <- plot.windrose(data = temp_wind_SACTN,
              spd = "spd",
              dir = "dir")

p.wr3 <- p.wr2 + facet_wrap(~ site) +
  theme(strip.text.x = element_text(size = 20))
p.wr3
```

@@

@@

temp_wind_SACTN <-  temp_wind_SACTN %>% 
  drop_na()

@@

temp.d <- temp.d(df = temp_wind_SACTN) 
# temp_wind_MUR <- temp_wind(df = MUR_fyears)
# temp_wind_SACTN <- temp_wind(df = SACTN_fyears)
# temp_wind_OISST <- temp_wind(df = OISST_fyears)
# temp_wind_G1SST <- temp_wind(df = G1SST_fyears)
# temp_wind_K10 <- temp_wind(df = K10_fyears)

@@

>>>>

## Load the sea surface temperatue datasets
## See the Dectect_MCS.Rmd script for more info. The datasets loaded here are only for temperatures collected between the years 1992-2016. However if a longer time series is required changes may  be made to the Dectect_MCS.Rmd script (line 136)

load("Data/overlap_ts.RData") # overlap: Sites within the SACTN dataset overlap, these sites 
load("Data/insitu_MUR.RData")
load("Data/insitu_OISST.RData")
load("Data/insitu_G1SST.RData")
load("Data/insitu_K10.RData")

@@

temp_wind_MUR <- temp_wind(df = MUR_fyears) %>% 
  drop_na()
temp_wind_SACTN <- temp_wind(df = SACTN_fyears)
temp_wind_OISST <- temp_wind(df = OISST_fyears)
temp_wind_G1SST <- temp_wind(df = G1SST_fyears)
temp_wind_K10 <- temp_wind(df = K10_fyears)

speed_plot <- temp_wind_MUR %>% 
  select(lat, lon, mean_speed) %>% 
  group_by(lat, lon) %>% 
  summarise(max_speed = max(mean_speed)) %>% 
  summarise(lat = round(lat, na.rm = T),3)#%>% 
  # dplyr::rename(Z = "mean_speed") %>% 
  # dplyr::rename(X = "lat") %>% 
  # dplyr::rename(Y = "lon")

 maxw <- cbind(speed_plot$lon, speed_plot$lat, speed_plot$max_speed)  
head(maxw)

rmax <- rasterFromXYZ(maxw)  
 acol <- colorRampPalette(c("white", "blue", "darkblue"))  
 plot(rmax, col=acol(1000), main= "Maximum wind speed reported",  
     xlab="Longitude", ylab="Lattitude")  + lines(getMap(resolution = "high"), lwd=2)

 library(rworldmap)  
 lines(getMap(resolution = "high"), lwd=2)  
```

@@

source("functions/wind.rose.R")
# 
# renaming_func <- function(df){
#   renaming <- df %>%
#   dplyr::rename(spd = mean_speed) %>%
#   dplyr::rename(dir = dir_circ)
# }
# 
# temp_wind_MUR <- renaming_func(df = temp_wind_MUR)
# # temp_wind_SACTN <- renaming_func(df = temp_wind_SACTN)
# # temp_wind_OISST <- renaming_func(df = temp_wind_OISST)
# # temp_wind_G1SST <- renaming_func(df = temp_wind_G1SST)
# # temp_wind_K10 <- renaming_func(df = temp_wind_K10)
# 
# ## Plotting function
# 
# p.wr2 <- plot.windrose(data = temp_wind_MUR,
#               spd = "spd",
#               dir = "dir")
# 
# p.wr3 <- p.wr2 + facet_wrap(~ site) +
#   theme(strip.text.x = element_text(size = 20))
# p.wr3
```

@@

For the wavelet analyses

@@

@@

#temp.d <- temp.d(df = temp_wind_SACTN)
# temp_wind_MUR <- temp_wind_MUR %>% 
#   drop_na()
# temp.d <- temp.d(df = temp_wind_MUR)
# temp_wind_OISST <- temp_wind_OISST %>% 
#   drop_na()
# temp.d <- temp.d(df = temp_wind_OISST)
# temp_wind_G1SST <- temp_wind_G1SST %>% 
#   drop_na()
# temp.d <- temp.d(df = temp_wind_G1SST)
# temp.d <- temp.d(df = temp_wind_K10)

@@

## Wind speed

```{r}
temp_wind_MUR <- temp_wind_MUR %>% 
    mutate(dir_circ = as.numeric(dir_circ))

SACTN_wind_dir <- ggplot(temp_wind_SACTN, aes(x = date)) +
  geom_path(aes(y = mean_speed)) +
  geom_path(aes(y = insitu_temp), colour = "orange") +
  facet_wrap(~ site, ncol = 1)  +
  # scale_y_continuous(breaks = c(10, 20, 30 ,40, 50), labels = c("10", "20", "30", "40", "50")) +
  theme_bw()
```

### 2019-03-15 wavelets.Rmd
progress..

* See the Dectect_MCS.Rmd script for more info. The datasets loaded here are only for temperatures collected between the years 1992-2016. However if a longer time series is required changes may  be made to the Dectect_MCS.Rmd script (line 136)

@@

SACTN_seasonal <- seasonal_col(df = SACTN_fyears)
MUR_seasonal <- seasonal_col(df = MUR_fyears)
OISST_seasonal <- seasonal_col(df = OISST_fyears)
G1SST_seasonal <- seasonal_col(df = G1SST_fyears)
K10_seasonal <- seasonal_col(df = K10_fyears)

@@

# creating a function to only select the year 2015
SST_season_func <- function(df){
seasonal_15 <- df %>% 
  filter(year == 2015 )
}

>>>>

* See the Dectect_MCS.Rmd script for more info. The datasets loaded here are only for temperatures collected between the years 1992-2016. However if a longer time series is required changes may  be made to the Dectect_MCS.Rmd script (line 136) . MCS using a long term time series to detect any extreme events occuring within the region

@@

# SACTN_seasonal <- seasonal_col(df = SACTN_fyears)
# MUR_seasonal <- seasonal_col(df = MUR_fyears)
# OISST_seasonal <- seasonal_col(df = OISST_fyears)
# G1SST_seasonal <- seasonal_col(df = G1SST_fyears)
# K10_seasonal <- seasonal_col(df = K10_fyears)

@@

# creating a function to only select the year 2015
SST_season_func <- function(df){
seasonal_15 <- df %>% 
  filter(year == 2015 )
}
seasonal <-  function(df)
